% !TEX root = ../oddp.tex

\section{Other considerations}

\begin{enumerate}
	\item These operations are compatible with suspension.
	\item Cup product is the Alexander cup product (possibly divided by a scalar).
	\item Succint description of the higher power operations.
	\item A measurement of the computational complexity of these operations.
	\item Comparison with previous formulas.
	%\item The case $r=2$. It is not trivial: $C^*(EC_2)\neq W^*(2)$.
	\item Naturality of the cup-i products. Bockstein. Cartan formulas. (I think we need them to axiomatically deduce that the power operations are the usual ones)
\end{enumerate}
\subsection{Compatibility with suspension} There standard suspension functor in the category of pointed semi-simplicial sets sends a semi-simplicial set $X_\bullet$ to the semi-simplicial set $(\Sigma X)_\bullet$ defined as:
\begin{align*}
    (\Sigma X)_n &= X_{n-1},& d_i(\Sigma\sigma) &= \Sigma d_{i+1}(\sigma),& d_{0}(\Sigma \sigma) &= *.
\end{align*}
Another possible and less standard definition of the suspension is the following:
\begin{align*}
    (\hat{\Sigma} X)_n &= X_{n-1}, &d_i(\hat{\Sigma}\sigma) &= \hat{\Sigma} d_i(\sigma),& d_{n+1}(\hat{\Sigma} \sigma) &= *.
\end{align*}
Similarly, we have the standard suspension of a chain complex $(C_*,\partial)$:
\begin{align*}
    (\Sigma C)_n &= C_{n-1}, & \partial (\Sigma c) = -\Sigma \partial c.
\end{align*}
and the less standard suspension:
\begin{align*}
    (\hat{\Sigma} C)_n &= C_{n-1}, & \partial (\hat{\Sigma} c) = \hat{\Sigma} \partial c.
\end{align*}
We also have that, for a semi-simplicial set $X_\bullet$ \begin{align*}
    \chains(\Sigma X)&\cong \Sigma \chains(X) & \chains(\hat{\Sigma}X) &\cong \hat{\Sigma}\chains(X)
\end{align*}

Now, if $\mu_{k}\colon \colon N_*(X)\to N_*(X)^{\otimes r}$ is the symmetric comultiplication in degree $k$, then we can define
\begin{align*}
    \Sigma \mu_k\colon \Sigma N_*(X)&\lra \Sigma N_*(X)^{\otimes r} 
    &
    \hat{\Sigma} \mu_k\colon \hat{\Sigma} N_*(X)&\lra \hat{\Sigma} N_*(X)^{\otimes r}
\end{align*}
which, under the above isomorphisms have the same domain and codomain as $\mu_{k+r-1}$.
\begin{proposition}
    \begin{align*}
        \Sigma \mu_k &= \rho(\mu_{k+r-1}) &
        \hat{\Sigma} \mu_k &= \mu_{k+r-1}
    \end{align*}
\end{proposition}
\begin{proof}
    Let $\tau$ be a generator of $N_m(X)$, so that \[\mu_k(\tau) = \mathrm{rev}\circ \alpha\circ\beta\circ\beta'\circ \Psi(e_{(r-1)m-k}^\vee\otimes \vec{\tau}).\]
    
    On the other hand, writing $\xi = \Sigma \tau$, we have 
    \[\mu_{k+r-1}(\Sigma \tau) = \mathrm{rev}\circ \alpha\circ\beta\circ\beta'\circ \Psi(e_{(r-1)(m+1)-(k-r+1)}^\vee\otimes \vec{\xi})\]
     Observe now that $k+r-1-(r-1)(m+1) = k-(r-1)m$, and therefore the words that will appear in the formulas for $\Psi(e_{(r-1)m-k}\otimes \vec{\tau})$ and $\Psi(e_{(r-1)m-k}\otimes \vec{\xi})$ are the same, while the sequences $U$ that appear in the formulas for $\Psi(e_{(r-1)m-k}\otimes \vec{\tau})$ are bounded by $m$ and the ones appearing in $\Psi(e_{(r-1)m-k}\otimes \vec{\xi})$ are bounded by $m+1$.
     
     Write $q = (r-1)m-k$.
     \[\Psi(e_{q}\otimes \vec{\tau}) = \sum_{U\in C^{q}(\Delta^m)}\sum_{w\in C^q(EC_r)} (U,w)\otimes \vec{\tau} \]
     Hence
     \begin{align*}
         \Sigma\Psi(e_{q}\otimes \vec{\tau}) 
         &= \sum_{U\in C^{q}(\Delta^m)}\sum_{w\in C^q(EC_r)} (\Sigma U,\rho(w))\otimes \vec{\tau} \\
         &= \sum_{U\in C^{q}(\Delta^m)}\sum_{w\in C^q(EC_r)} (U,\rho(w))\otimes \vec{\tau} \\
         &= \Psi(\rho(e_q^\vee)\otimes \vec{\tau})
    \end{align*}
    In the first equality we had to take $\rho(w)$ (recall that this is a dual action, hence $\rho(a) = a-1$) to counteract the effect of $\Sigma$ on $U$, which reindexes the indices by one up. In the second equality we use that any $U$ containing a $0$ yields a trivial summand because in $\Sigma X$ the face map $d_0$ sends everything to the basepoint. This proves the first claim, and an analogous argument proves the second claim. 
\end{proof}
\subsection{REV} \subsection{A reordering} Consider the $r$-fold tensor product $\chains(\Delta^n)^{\otimes r}$ with the backwards cyclic action of $C_r$:
\[\rho(U_0\otimes \ldots\otimes U_{r-1}) = U_1\otimes \ldots \otimes U_{r-1}\otimes U_0\]
and the forward cyclic action:
\[\rho(U_0\otimes \ldots\otimes U_{r-1}) = U_{r-1}\otimes U_0\otimes \otimes \ldots \otimes U_{r-2}.\]
Let $\mathrm{rev}\colon N_*(\Delta^n)^{\otimes r}\to N_*(\Delta^n)^{\otimes r}$ be the $C_r$-equivariant homomorphism that sends a product $(\tau_0\otimes\ldots\otimes \tau_{r-1})$ to the product $(-1)^{\xi(\tau_{0},\ldots,\tau_{r-1})}(\tau_{r-1}\otimes\ldots\otimes \tau_0)$, where $\xi(\tau_0,\ldots,\tau_{r-1})$ is the Koszul sign associated to the reversal.
\begin{example}\label{ex:101}
    If $r=3$ and $(\tau_0,\tau_1,\tau_2) = [0,2,3]\otimes [3,4,5] \otimes [5,7,9]$, then its reversal is $-[5,7,9]\otimes [3,4,5]\otimes [0,2,3]$.
\end{example}


\subsection{Alexander product} Recall that a semi-simplicial set $X$ can be viewed as an augmented semi-simplicial pointed set $X_+$ by taking augmening $X$ with the basepoint. 

The operation induced in degree $0$
\[\mu_0\colon N_m(\Delta^n)\lra (N_*(\Delta^n)^{\otimes r})_m\]
is indexed by words of length $m(r-1)$, with the coefficient $\frac{1}{(\tilde{r}!)^m}$ and a CERTAIN SIGN TO BE COMPUTED. As observed before, $\tilde{r}!\mod r$ is one of the two square roots of $-1$. Moreover, since $\Delta^n$ is augmented with the basepoint, all summands of $\mu_0(\tau)$ that involve elements of degree $0$ are automatically zero in $\Delta^n$ (but not in $\Delta^n_+$). Say that those elements are \emph{suboptimal}. A word $(w_0,w_1,\ldots,w_q)$ in $EC_r$ is \emph{ascending} if $w_{i+1} = w_i+1\mod r$. 

\begin{proposition}
    The non-suboptimal summands in $\mu_0(\tau)$ are those indexed by ascending words.
\end{proposition}
\begin{proposition}
    The non-suboptimal summands indexed by ascending words form the Alexander diagonal. The sign is as follows: BLABLA 
\end{proposition}
\begin{corollary}
    $\mu_0$ is the usual diagonal. [I highly doubt that we get the same signs]
\end{corollary}




\subsection{Augmentations} It is remarkable that these operations extend to the category of augmented (pointed) semi-simplicial sets, something that was not available through the surjection operad description.  

\subsection{Power operations} A symmetric comultiplication induces power operations 
\[P^k\colon H^*(\Delta^n)\to \Sigma^{-k} H^*(\Delta^n)\]
defined as $P^k(x) =\nu(m)\cdot \mu_{(r-1)m-k}^*(x\otimes x\otimes\ldots\otimes x)$. In our case the action of $C_r$ on $N(\Delta^n)^{\otimes r}$ factors through the action of the symmetric group $\Sigma_r$, and therefore only some of these operations survive. 
\federico{Here $\nu(m) = \frac{1}{(\tilde{r}!)^m}$}

\section{To be discarded}
\subsection{Comparison with the surjection operad (drafty)}

Consider the functor tensor product $F^*\otimes G$, that is, $N_*(\Delta^\bullet)\otimes_\Delta N_\bullet(\Delta^n)$. It is related to the previous tensor product via Poincaré duality and it is isomorphic to $N_*(\Delta^n)^{\otimes r}$. Similarly, there is a chain complex analogous to $\Omega(r,n)$ that we denote, for the moment as $\Omega^\vee(r,n)$. Instead of using the previous isomorphism, we will use the isomorphism that sends $u_i\in U$ to the $w_i$-th factor of the tensor product.

If $\tau$ is a simplex of dimension $m$, one consider all pairs $(f,A)$ where
\begin{itemize}
	\item $f$ is a surjection, i.e., a non-degenerate word in $EC_r$ that contains every element $0,1,\ldots,r-1$ at least once.
	\item $A$ is a decomposition of a simplex $\tau$ into overlapping intervals.
\end{itemize}
Now,
\begin{itemize}
	\item The pair $(f,A)$ defines a word in $EC_r$ given by replicating each number in $f$ as many times as the length of each interval dictates. For example, if $r=3$ and $f= 0121012$ and $A=(0,1,2)(2)(2,3)(3)(3,4,5)(5,6)(6)$, then the resulting word is $w=0001221000112$.
	\item $A$ gives a simplex in $\Delta^m$ that results from erasing the parentheses: $U=[0,1,2,2,2,3,3,3,4,5,5,6,6]$
\end{itemize}
The triple $(f,A,\tau)$ thus yields an element of $\Omega^\vee(r,n)$, whose image coincides with the image of the operation $(f,A)$ on $\tau$.

If we want to interpret this element in $\Omega(r,n)$, we just need to do the following:
\begin{itemize}
	\item The new $U$ is obtained from the maximally degenerate simplex \[(0,0,0,1,1,1,2,2,2,3,3,3,4,4,4,5,5,5,6,6,6)\] by removing the elements of $U$. In our case, $U=(0,0,1,1,4,4,5,6)$.
	\item The new $w$ is obtained from $w$ by setting $w_i$ equal to any element of $C_r$ different from the ones that where labeling $u_i$ in the old $w$ \emph{provided that the old ones were not repeated. Otherwise, the operation is zero!!. Nonetheless, these cases may be easily identified}. This happens quite often. In our case $w=(12121220)$.
\end{itemize}
Finally, we need to substract $u_i$ from $w_i$ to obtain the word we care about in $\Omega(r,n)$: (12010100)

If $f$ is a surjection, let $w$ be the pieced word that comes from replacing each entry by its complement. Let $Q(f)$ be the collection of all subwords of all representatives of $w$.
\begin{lemma} In this dictionary (without the last substraction), the collection of words associated to a surjection $f$ is $Q(f)$.
\end{lemma}

\subsection{The even prime [TO BE DELETED]} This strategy can be also applied to recover the presentation in [ANIBAL] of the classical formulas of Steenrod for the cup-$i$ products. All the maps remain the same except for $\varphi\colon W_*(r)\otimes N_*(\Delta^n)\to \WW^*(r)\otimes N^r_*(\Delta^n)$, which is no longer well-defined because $(r-1)m$ is not always even. To remedy this handicap, consider the other (suspended) resolution $\VV_*(2)$ of $C_2$:
\[R\langle C_2\rangle \overset{T-1}{\lra} R\langle C_2\rangle \overset{1+T}{\lra} R\langle C_2\rangle \overset{T-1}{\lra} R.\]
There is a flip map $\varphi_k\colon W_*(2)\to \VV^*(2)$ for every odd $k$, and there are suspension maps $\theta\colon \WW^*(r)\to \Sigma \VV^*(r)$ and $\theta\colon \VV^*(r)\to \Sigma \WW^*(r)$ that send a generator $e_q$ to $e_{q-1}$. Consider the complex
\[\mathbf{U}^*(2,n) = \bigoplus_{m\text{ odd}} \VV^m(r)\otimes N^2_m(\Delta^n)
oplus
\bigoplus_{m\text{ even}} \WW^m(r)\otimes N^2_m(\Delta^n)
\]
with differential $\partial(e_q^\vee\otimes \vec{\tau}) = \partial(e_q^\vee)\otimes \vec{\tau} + (-1)^q \theta(e_q)\otimes \partial \vec{\tau}$. Define
\[\varphi\colon \varphi\colon W_*(r)\otimes N_*(\Delta^n)\to 
\mathbf{U}^*(2,n)\]
as $\varphi(e_q\otimes \tau) = \varphi_m(e_q)\otimes \vec{\tau}$.

In this case $\Theta(2,n) = \NN^*(\Delta^\bullet)\otimes_{\Delta} N_*^2(\Delta^n)$. Define a map $\Psi\colon U^*(2,n)\to \Theta(2,n)$ as $e_q\otimes \vec{\tau}\mapsto \Psi(e_q)\otimes \vec{\tau}$ where 
\begin{align*}
    \WW^*(r)\lra N^*(EC_r) \lra N^*(\Delta^n\times EC_r) \\
    \VV^*(r)\lra N^*(EC_r) \lra N^*(\Delta^n\times EC_r) \\
\end{align*}
{color{red}THIS DOES NOT WORK. I think twisted coefficients might be needed}
